Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-04-02 parts/intro.tex
update notations

\paragraph*{Notations}
We denote: $\segm{a}{b} = \{ a, a+1, \dots, b-1, b \}$.
If $A$ is a finite set,
$|A|$ is the cardinality of $A$
and $\powerset(A)$ is the power set of $A$.
If $x = (x_i)_{i \in \segm{a}{b}}$ is a sequence of elements indexed by $i \in \segm{a}{b}$,
we denote $|x| = (b-a)+1$ the size of this sequence
and $\indexes{x} = \segm{1}{|x|}$ its set of indexes.
We also denote by $\emptyseq$ the empty sequence.
If $A$ and $B$ are sets,
$f : A \rightarrow B$ denotes an application $f$ that maps elements of $A$ to elements of $B$.
Finally, $\lfp{x_0}{x}{x'}$ is the least fixed point greater that $x_0$ of the function $x \mapsto x'$.

>>>>

\paragraph*{Notations}
%We denote: $\segm{a}{b} = \{ a, a+1, \dots, b-1, b \}$.

If $A$ is a finite set,
$|A|$ is the cardinality of $A$
and $\powerset(A)$ is the power set of $A$.
If $x = (x_i)_{i \in \segm{1}{n}}$ is a sequence of elements indexed by $i \in \segm{1}{n}$,
%we denote %$|x| = (b-a)+1$ the size of this sequence and
$\indexes{x} = \segm{1}{n}$ is the set of indexes of this sequence.
We also denote by $\emptyseq$ the empty sequence.
If $A$ and $B$ are sets,
$f : A \rightarrow B$ denotes an application $f$ that maps elements of $A$ to elements of $B$.
$\lfp{x_0}{x}{x'}$ is the least fixed point greater that $x_0$ of the function $x \mapsto x'$.
